\section{Research Question}

Nikhef deals with enormous amounts of data to transport and process. For this reason they own servers that can handle these amounts of data. The amount of data keeps on growing and the specs of the servers are also keep getting better and better. Interfaces of 100GBe are nothing new. 
Security measurements need to be scaled to these levels as well. A security device needs to be able to handle the cumulation of the flows going trough the security device. The specs of the machines are measured in the same way. The term used for this is IMIX, this is short for Internet Mix. This should resemble the traffic that can be seen in "real-world" conditions. This is all valid and "pretty" traffic. But the real world traffic is not always "pretty". A lot of attacks are performed daily. Therefore the need for a tool that gives the administrator the opertunity to test a machine on higher bandwiths that the regular tools. This brings us to the research question that will drive this research. 
  
\textbf{The research question is as follows:}\\
Where are the current limitations for traffic generation in order to test real world DDOS attacks on machines.

\textbf{This question contains a couple topics that need to be addressed}\\
\begin{itemize}
\item{What is the current maximum bandwith and how is this maximum reached?}
\item{What available techniques are out there to generate traffic?}
\item{How can a system be stressed in an optimal way to make it crash?}
\end{itemize}

